
## Load the data
```{r, echo=TRUE}
rawdata <- read.csv("activity.csv", header = T, stringsAsFactors = F)
dim(rawdata)
```

## Transform the data
```{r, echo=TRUE}
 noNA <- rawdata[complete.cases(rawdata),]
 dim(noNA)
 ```
 
## mean total number of steps taken per day
 
 ```{r, echo=TRUE}
 library(ggplot2)
 ggplot(noNA, aes(as.factor(date),steps))+geom_bar(fill="green", stat="identity")+
   xlab("Day") + ylab("Steps")+ggtitle("Histogram of the total number of steps taken each day")+
   theme(axis.text.x = element_text(angle = 90, hjust = 2))
   ```
   
## Calculate the mean of the total number of steps taken per day

  ```{r, echo=TRUE}
   meanFreq <- as.integer(mean(aggregate(steps~date,noNA, FUN=sum)$steps))
   meanFreq
 ```

##  Calculate the median of the total number of steps taken per day
```{r, echo=TRUE}
 medianFreq <- median(aggregate(steps~date,noNA, FUN=sum)$steps)
 medianFreq
 ```
 
 ##  What is the average daily activity pattern

 ```{r, echo=TRUE}
q2 <- aggregate(steps~interval, noNA, FUN=mean)
plot(q2$steps ~ q2$interval, type="l", xlab="Date", ylab="Average Steps per Day (5-mins interval")
```
## Imputing missing values

```{r, echo=TRUE}
numNA <- nrow(rawdata) - nrow(noNA)
imputedata <- rawdata
meanNA <- aggregate(steps~interval,imputedata, FUN=mean)
for(i in 1:nrow(imputedata)){
  if(is.na(imputedata[i,c("steps")])){
    imputedata[i,c("steps")] <- meanNA[meanNA$interval==imputedata[i,c("interval")], c("steps")]
  }
}
ggplot(imputedata,aes(as.factor(date),steps))+geom_bar(fill="green", stat="identity")+xlab("Day") + ylab("Steps")+ggtitle("Histogram of the Total Number of Steps Taken Each Day (Imputed Data)")+ theme(axis.text.x = element_text(angle = 90, hjust = 2))
```

## Calculate  the mean and median total number of steps taken per day

```{r, echo=TRUE}
newmeanfreq <- as.integer(mean(aggregate(steps~date, imputedata, FUN = sum)$steps))
newmeanfreq
newmedianfreq <- median(aggregate(steps~date, imputedata, FUN = sum)$steps)
newmedianfreq
```
*1 There is no diffrence between old meanFreq value and new meanfreq value.
*2 There is .66 diffrence between old median value and new median value.


# differences in activity patterns between weekdays and weekends

```{r, echo=TRUE}
weekDayEnd <- data.frame("dayType"=character(0))
weekDayEnd <- NULL

#Check wether the day is a weekday or weekend (Saturday)
weekInd <- function(day){
  if (weekdays(day)=="Saturday") {
    out <- "Weekend" 
  } else {
    out <- "Weekday" 
  }
  out
}

for (i in 1:nrow(imputedata)){
  date <- imputedata[i,c("date")]
  newObs <- data.frame("dayType"= weekInd(as.Date(date)))
  weekDayEnd <- rbind(weekDayEnd, newObs)
}
```

#Add the day type column in the data set
```{r, echo=TRUE}
imputedata <- cbind(imputedata, weekDayEnd)
averageWeekDayEnd<-aggregate(steps~interval + dayType, imputedata, FUN=mean)
ggplot(averageWeekDayEnd,aes(interval,steps, color=dayType))+geom_line()+facet_wrap(~dayType, ncol=1)+xlab("5-min Interval")+ylab("Steps")+guides(fill=FALSE) 
```


